\chapter{Protocol design}\label{ch:proto}

The implementation of the protocol can be found in the \code{common/protocol.c}
file.

Through this module, the application (either the client or the server) can send
and receive three different type of messages:
\begin{enumerate}
	\item \standout{Plain message}: a plaintext message. These messages are
		used only by the server to send its public certificate to the
		client;
	\item \standout{Signed message}: a plaintext message with a signature
		appended to it. The signature is generated using the \openssl{}
		EVP API with SHA-256 as hashing algorithm and RSA as signing
		algorithm. These messages are used before the GCM initialization
		during the key establishment process described in
		\secref{sec:keyxchng};
	\item \standout{GCM encrypted message}: a message encrypted and
		authenticated with GCM AES-128. These messages are used when the
		GCM module has been initialized after a session key has been
		established.
\end{enumerate}

All the messages exchanged by the application, regardless of their type, are
prefixed with the header, of a total size of 49 bytes, shown
in~\lstref{lst:msgheader}.

\lstinputlisting[language=c, label={lst:msgheader}, caption={Header prefixed to
each message of the application}]{msgheader.c}

Here, we describe each field of the header and their use:
\begin{itemize}
	\item[\standout{magic}] \emph{(4 bytes)} A magic number, always equal to
		\code{0xDECODE}.  It is used to ensure that the received message
		has a valid header;
	\item[\standout{counter}] \emph{(4 bytes)} An incremental message
		counter. It starts from \(1\) and it's incremented for each
		message sent. It is used to avoid replay attacks;
	\item[\standout{type}] \emph{(1 byte)} The message type, used to convert
		the payload to the correct data structure;
	\item[\standout{payload\_size}] \emph{(4 bytes)} Total payload size. For
		the usage of this field, see below;
	\item[\standout{nonce}] \emph{(4 bytes)} A random 4 bytes integer. It is
		use manly to add randomness to the message (why this is useful
		is explained in \secref{sec:keyxchng}. It is also used (among
		other variables) to derive a new initialization vector for GCM
		after each message exchanged (see \secref{sec:protosecurity} for
		details);
	\item[\standout{prev\_hash}] \emph{(32 bytes)}SHA-256 hash of the last
		received message.  This is used for the security of signed
		messages. See \secref{sec:protosecurity} for details.
\end{itemize}

Before GCM initialization the receiver can extract the total length of any
message by just reading the message header (of fixed size) from the socket and
then read the entire payload of size equal to \code{header.payload\_size}.

In case of signed messages, after the message (with header and payload), the
sender appends a 4 byte integer, which represents the size of the signature, and
the signature.

In case of GCM encrypted messages, the GCM tag (with a fixed size of 16 bytes)
is appended after the message.

After GCM initialization, since the messages are encrypted, there is no way for
the receiver to extract the header without knowing \emph{a priori} the size of
the entire message.

In this case, if the total message size (header plus payload) is larger than 128
bytes, the message is split into two smaller messages: the first with a total
size of 128 bytes; the second with a variable size (the header plus the
remaining payload). An header is prefixed to both messages.

If the total message size is lower than 128 bytes, the payload is padded with
zeroes until a size of 128 total bytes is reached. The padding portion of the
payload can be separated by the useful data by evaluating the
\code{payload\_size} field of the header.

This ensures that, in case of GCM message, the receiver always gets a message of
128 bytes. Then, it can determine the size of the eventual second GCM message by
reading the \code{payload\_size} field of the header.

\input{proto/security}
\input{proto/keyxchng}
