\section{Client modules}\label{sec:clientmod}

This section describes the modules of the client. For further reference, the
code can be found in the \code{client} folder.

\subsection{X509}\label{subsec:clientx509mod}

This module allows to deserialize and verify (against the trusted authority's CA
and CRL files) the certificate received by the server.

\subsection{Proto}\label{subsec:clientprotomod}

This modules builds the messages that must be sent to the server or the
opponent's client during a game. It also calls the functions of the common
library's \code{protocol} module to effectively send/receive the messages.

\subsection{Console input (cin)}\label{subsec:cinmod}

This module contains functions used to correctly read from the Standard Input.

\subsection{Main module}\label{subsec:clientmainmod}

\ldots

\subsection{Game modules}\label{subsec:gamemods}

This section analyzes the describes the modules that implement the game logic
and the peer-to-peer communication during a game.

\subsubsection{Connect 4}

It contains function to initialize the board, check if one of the two players
has won the game after each move and print the board. It also tracks which is
the current active player.

\subsubsection{Game}

This module sets up and manages the game between the player and its opponent. At
the beginning of the game, it initialized a secure session with the other party.
Then, it handles the input from the player when he makes a move in the game and
the messages coming from the opponent.

It uses the \code{Connect 4} module to register each move made in the game and
print the board after each move.
